Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_wrapping.tex
figures added
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@855 d8b0c59b-6544-0410-94d9-83a5658a058e

%This section talks about the service wrapper tool (Kassel prototype)
%
%What it offers (afaik now it supports RESTful services, if support for SOAP-based services is also implemented, talk about it, otherwise explain how you expect to address it in the future work section
%
%How to create a wrapper (test-and-construct approach)
%
%Place this component within the FAST architecture
%
%Talk about formats: JSON and XML??

@@

As a first approach, the interaction with services is limited to simple GET requests as supported e.g. by REST services. Support for other services like SOAP services is planned. A service request is thus assembled using a certain URL and a set of parameters. As an example, the Ebay Shopping web service will be studied. The following URL is invoked to retrieve a list of items corresponding to the search keywords \emph{USB}.

\url{http://open.api.sandbox.ebay.com/shopping?appid=KasselUn-efea-4b93-9505-5dc2ef1ceecd&version=517&callname=FindItems&ItemSort=EndTime&QueryKeywords=USB&responseencoding=XML}

As you may see, the URL invoked is http://open.api.sandbox.ebay.com/shopping and the parameters used in the example are:
\begin{description}
	\item[appid] this is the application ID obtained to use the API.
	\item[version] the API version.
	\item[callname] in this case FindItems to search through all items in Ebay.
	\item[itemsort] sorting method for the list of items.
	\item[querykeywords] list of keywords.
	\item[responseencoding] format of the response message obtained by the invocation of the request.
\end{description}

@@

%\begin{figure}
%  \begin{center} \includegraphics[width=\linewidth]{images/ServiceWrapperToolGVSWithPortDefinitions.jpg}
%    \caption{Configuring parameters of a service wrapper (photoshoped screen dump)}
%    \label{fig:construct_pre_post_conditions}
%  \end{center}
%\end{figure}

@@

Figure ~\ref{fig:construct_service_request} shows the web based tool to construct the service requests.

%\begin{figure}
%  \begin{center}
%    \includegraphics[width=\linewidth]{images/ServiceWrapperToolGVSWithRequestExample.jpg}
%    \caption{Constructing the service request URL and its parameters (photoshoped screen dump)}
%    \label{fig:construct_service_request}
%  \end{center}
%\end{figure}

@@

%\begin{figure}
%  \begin{center}
%      \includegraphics[angle=90,width=0.8\linewidth]{images/ServiceWrapperToolGVSWithTransformationRules.jpg}
%    \caption{Interactive, rule based transforming of an XML response to domain objects (photoshoped screen %dump)}
%    \label{fig:response_service_execution}
%  \end{center}
%\end{figure}

>>>>

@@

As a first approach, the interaction with services is limited to simple GET requests as supported e.g. by REST services. Support for other services like SOAP services is planned. A service request is thus assembled using a certain URL and a set of parameters. As an example, the Ebay Shopping web service will be studied. The following URL is invoked to retrieve a list of items corresponding to the search keywords \emph{USB}:

\begin{listing}
\begin{verbatim}
http://open.api.sandbox.ebay.com/shopping?appid=KasselUn-efea-4b93-9505-5dc2ef1ceecd
  &version=517&callname=FindItems&ItemSort=EndTime&QueryKeywords=USB&responseencoding=XML
\end{verbatim}
\end{listing}

As you may see, the URL invoked is \url{http://open.api.sandbox.ebay.com/shopping} and the parameters used in the example are:
\begin{description}
	\item[appid] this is the application ID obtained to use the API.
	\item[version] the API version.
	\item[callname] in this case FindItems to search through all items in Ebay.
	\item[itemsort] sorting method for the list of items.
	\item[querykeywords] list of keywords.
	\item[responseencoding] format of the response message obtained by the invocation of the request.
\end{description}

@@

\begin{figure}
  \begin{center} \includegraphics[width=\linewidth]{images/ServiceWrapperToolGVSWithPortDefinitions.png}
    \caption{Configuring parameters of a service wrapper}
    \label{fig:construct_pre_post_conditions}
  \end{center}
\end{figure}

@@

Figure~\ref{fig:construct_service_request} shows the web based tool to construct the service requests.

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{images/ServiceWrapperToolGVSWithRequestExample.png}
    \caption{Constructing the service request URL and its parameters}
    \label{fig:construct_service_request}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{images/ServiceWrapperToolGVSWithTransformationRules.png}
    \caption{Interactive, rule based transforming of an XML response to domain objects}
    \label{fig:response_service_execution}
  \end{center}
\end{figure}
